---
title: "11 human primary breast cancer tumors"
subtitle: "GEO accession number: GSE75688" 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

# Sample info
### 57915 genes and 547 cells
### 11 integrated samples

```{r, message=FALSE, warning=FALSE}
library(TMExplorer)
library(scater)
library(scran)
library(uwot)
library(plotly)
library(dplyr)

source("D:/Users/George/Desktop/rnaSEQ/TME_scRNAseq_workflow/scripts/utilities.R")

sce <- readRDS("D:/Users/George/Desktop/rnaSEQ/TME_scRNAseq_workflow/GSE75688/sce.rds")
colour_list <- c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F", "#E5C494", "#B3B3B3", '#E2201C', '#1D91C0', '#6B3E9A', '#32A028', "deepskyblue", "black")

```


```{r, message=FALSE, warning=FALSE}

gene_name <- "TNFSF4_ENSG00000117586.6"

df_tsne <- make_df(sce, "TSNE", gene_name)
p1 <- make_plots_2d(sce, df_tsne, "cluster", "TSNE", colour_list)
p2 <- make_plots_3d(sce, df_tsne, "cluster", "TSNE", colour_list)
p3 <- make_plots_2d(sce, df_tsne, "celltype", "TSNE", colour_list)
p4 <- make_plots_2d(sce, df_tsne, gene_name, "TSNE", colour_list)

df_pca <- make_df(sce, "PCA", gene_name)
p5 <- make_plots_2d(sce, df_pca, "cluster", "PCA", colour_list)
p6 <- make_plots_3d(sce, df_pca, "cluster", "PCA", colour_list)
p7 <- make_plots_2d(sce, df_pca, "celltype", "PCA", colour_list)
p8 <- make_plots_2d(sce, df_pca, gene_name, "PCA", colour_list)

p9 <- filter_and_plot(df_tsne, 3, "celltype", gene_name)
p9.1 <- filter_and_plot(df_tsne, 2, "celltype", gene_name)
p9.2 <- filter_and_plot(df_tsne, 1, "celltype", gene_name)
p9.3 <- filter_and_plot(df_tsne, 0, "celltype", gene_name)

expressionmean = aggregate(.~celltype, df_tsne[,-c(1:4)], mean)
```

# TSNE PLOTS
## TSNE plots showing clusters and celltypes
```{r, message=FALSE, warning=FALSE}

p1
p2
p3

```

## TSNE plot showing the gene counts - "TNFSF4_ENSG00000117586.6"
```{r, message=FALSE, warning=FALSE}

p4

```

# PCA PLOTS
## PCA plots showing clusters and celltypes 
```{r, message=FALSE, warning=FALSE}

p5
# p6
p7

```

## 2D PCA plot showing the gene counts - "TNFSF4_ENSG00000117586.6"
```{r, message=FALSE, warning=FALSE}

p8

```

## Number of cells from each cell type in the sample
### Data filtered to only keep cells with more than 3 transcripts per cell down to all cells
```{r}

p9
p9.1
p9.2
p9.3

```

```{r}

p10 = barplot(expressionmean$TNFSF4_ENSG00000117586.6, names.arg=expressionmean$celltype, main="Average expression per cell", col = colour_list)

```